Lexicographic exponentiation: An example of proof documentation with Alectryon

### 2021-11-20 doc/tuto.tex
fix  typos

\subsubsection{Second case}
Let us consider a well formed list \texttt{y} of the form \texttt{(b,p)::l'}, where \texttt{ltA b a}. By \texttt{IHa}, this list is accessible.

@@

\subsubsection{Third case}
The list \texttt{y} may be of the form  \texttt{(a,n)::l'}, where \texttt{LT l' l}. By \texttt{H2},  \texttt{y} is accessible.

@@

\subsubsection{Last case}
The list \texttt{y} may be of the form  \texttt{(a,p)::l'}, where \texttt{p<n}. Thus, we may apply \texttt{Hn}.

>>>>

\subsubsection{Second case}
Let us consider a well formed list \texttt{y} of the form \texttt{(b,p)::l''}, where \texttt{ltA b a}. By \texttt{IHa}, this list is accessible.

@@

\subsubsection{Third case}
The list \texttt{y} may be of the form  \texttt{(a,n)::l''}, where \texttt{LT l'' l}. By \texttt{H2},  \texttt{y} is accessible.

@@

\subsubsection{Last case}
The list \texttt{y} may be of the form  \texttt{(a,p)::l''}, where \texttt{p<n}. Thus, we may apply \texttt{Hn}.
